---
title: "Figure Scripts"
author: "LucianoRogerio"
date: "2022-01-25"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


## Results IITA Breeding Scheme Simulation with and without Genomic Selection


### F1

```{r, eval = F}
library(here); suppressMessages(library(tidyverse))

postBurnInIITAGS <- readRDS(here::here("output", "postBurnIn_IITA_GS.rds"))
postBurnInIITAPS <- readRDS(here::here("output", "postBurnIn_IITA_PS.rds"))

forSimPlotIITAF1 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_longer(SimOutput) %>%
              filter(SimOutput_id == "records") %>%
              mutate(records = SimOutput) %>%
              select(SimRep, PostBurnIn, records) %>% 
              unnest_longer(records) %>%
              filter(records_id == "stageOutputs") %>%
              mutate(stageOutputs = records) %>%
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter(stage == "F1") %>%
  mutate(YearPostBurnIn = year - 20)

saveRDS(forSimPlotIITAF1, here::here("output", "DataSimPlotIITA_F1.rds"))
rm(forSimPlotIITAF1)
```

### Parents

```{r, eval = FALSE}

forSimPlotIITAPar <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_longer(SimOutput) %>%
              filter(SimOutput_id == "records") %>%
              mutate(records = SimOutput) %>%
              select(SimRep, PostBurnIn, records) %>% 
              unnest_longer(records) %>%
              filter(records_id == "PopImprov") %>%
              select(SimRep, PostBurnIn, records) %>% 
              unnest(cols = records) %>% 
  mutate(YearPostBurnIn = year - 20)

saveRDS(forSimPlotIITAPar, here::here("output", "DataSimPlotIITA_Par.rds"))
rm(forSimPlotIITAPar)
```
### Last Stage

```{r, eval = F}
forSimPlotIITAUYT2 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_longer(SimOutput) %>%
              filter(SimOutput_id == "records") %>%
              mutate(records = SimOutput) %>%
              select(SimRep, PostBurnIn, records) %>% 
              unnest_longer(records) %>%
              filter(records_id == "stageOutputs") %>%
              mutate(stageOutputs = records) %>%
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter(stage == "UYT2") %>%
  mutate(YearPostBurnIn = year - 20)

saveRDS(forSimPlotIITAUYT2, here::here("output", "DataSimPlotIITA_UYT2.rds"))
rm(postBurnInIITAGS); rm(postBurnInIITAPS); rm(forSimPlotIITAUYT2)
```


## Results IITA 1ยบ alternative Breeding Scheme Simulation with and without Genomic Selection


### F1

```{r, eval = F}
library(here); suppressMessages(library(tidyverse))

postBurnInIITAGS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_GS.rds"))
postBurnInIITAPS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_PS.rds"))

forSimPlotIITA_NVDP_F1 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_wider(SimOutput) %>% 
              select(SimRep, PostBurnIn, records) %>% 
              unnest_wider(records) %>% 
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter(stage == "F1") %>%
  mutate(YearPostBurnIn = year - 20)

saveRDS(forSimPlotIITA_NVDP_F1, here::here("output", "DataSimPlotIITA_NVDP_F1.rds"))
rm(forSimPlotIITA_NVDP_F1)
```


### Last Stage

```{r, eval = F}
postBurnInIITAGS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_GS.rds"))
postBurnInIITAPS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_PS.rds"))

forSimPlotIITA_NVDP_UYT1 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_wider(SimOutput) %>% 
              select(SimRep, PostBurnIn, records) %>% 
              unnest_wider(records) %>% 
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter((stage == "UYT2" & year < 20) | (stage == "UYT1" & year >= 20)) %>%
  mutate(YearPostBurnIn = year - 20)

saveRDS(forSimPlotIITA_NVDP_UYT1, here::here("output", "DataSimPlotIITA_NVDP_UYT1.rds"))
rm(postBurnInIITAGS); rm(postBurnInIITAPS); rm(forSimPlotIITA_NVDP_UYT1)
```

## Results IITA 2ยบ alternative Breeding Scheme Simulation with and without Genomic Selection


### F1

```{r, eval = F}
library(here); suppressMessages(library(tidyverse))

postBurnInIITAGS <- readRDS(here::here("output", "postBurnIn_NVDP2_IITA_GS.rds"))
postBurnInIITAPS <- readRDS(here::here("output", "postBurnIn_NVDP2_IITA_PS.rds"))

forSimPlotIITA_NVDP2_F1 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_wider(SimOutput) %>% 
              select(SimRep, PostBurnIn, records) %>% 
              unnest_wider(records) %>% 
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter(stage == "F1") %>%
  mutate(YearPostBurnIn = year - 20)



saveRDS(forSimPlotIITA_NVDP2_F1, here::here("output", "DataSimPlotIITA_NVDP2_F1.rds"))
rm(forSimPlotIITA_NVDP2_F1)
```


### Last Stage

```{r, eval = F}
postBurnInIITAGS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_GS.rds"))
postBurnInIITAPS <- readRDS(here::here("output", "postBurnIn_NVDP_IITA_PS.rds"))

forSimPlotIITA_NVDP2_AYT <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_wider(SimOutput) %>% 
              select(SimRep, PostBurnIn, records) %>% 
              unnest_wider(records) %>% 
              select(SimRep, PostBurnIn, stageOutputs) %>% 
              unnest(cols = stageOutputs) %>% 
              filter((stage == "UYT2" & year < 20) | (stage == "AYT" & year >= 20)) %>%
  mutate(YearPostBurnIn = year - 20)
table(forSimPlotIITA_NVDP2_AYT$year, forSimPlotIITA_NVDP2_AYT$stage)

saveRDS(forSimPlotIITA_NVDP2_AYT, here::here("output", "DataSimPlotIITA_NVDP2_AYT.rds"))
rm(postBurnInIITAGS); rm(postBurnInIITAPS); rm(forSimPlotIITA_NVDP2_AYT)
```

## Joint all the data in two files

One for F1 results, and one for the last stage of it breeding scheme

### F1 Results
```{r, eval = TRUE}
library(here); suppressMessages(library(tidyverse))

IITA_F1 <- readRDS(here::here("output", "DataSimPlotIITA_F1.rds"))
NVDP1_F1 <- readRDS(here::here("output", "DataSimPlotIITA_NVDP_F1.rds"))
NVDP2_F1 <- readRDS(here::here("output", "DataSimPlotIITA_NVDP2_F1.rds"))

F1Res <- IITA_F1 %>% mutate(BreedScheme = "IITA") %>%
  bind_rows(NVDP1_F1 %>%
              mutate(BreedScheme = "NVDP1")) %>%
  bind_rows(NVDP2_F1 %>% mutate(BreedScheme = "NVDP2"))

saveRDS(F1Res, file = here::here("output", "F1ResultsIITA.rds"))
```

### Last Stage Results
```{r, eval = TRUE}

IITA_UYT2 <- readRDS(here::here("output", "DataSimPlotIITA_UYT2.rds"))
NVDP1_UYT1 <- readRDS(here::here("output", "DataSimPlotIITA_NVDP_UYT1.rds"))
NVDP2_AYT <- readRDS(here::here("output", "DataSimPlotIITA_NVDP2_AYT.rds"))

LSRes <- IITA_UYT2 %>% mutate(BreedScheme = "IITA") %>%
  bind_rows(NVDP1_UYT1 %>%
              mutate(BreedScheme = "NVDP1")) %>%
  bind_rows(NVDP2_AYT %>% mutate(BreedScheme = "NVDP2"))

saveRDS(LSRes, file = here::here("output", "LastStageResultsIITA.rds"))
```


## Simulations IITA Breeding Scheme - 1-3 Years as candidates
```{r Joint data of Sim 1-3 years, eval = FALSE}

schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")

IITAPS  <- readRDS(here::here("output", "postBurnIn_IITA_PS.rds"))
IITAPSPlus  <- readRDS(here::here("output", "postBurnIn_IITA_PSPlus.rds"))
IITA1Yr <- readRDS(here::here("output", "postBurnIn_IITA_GS_1Yr.rds"))
IITA2Yr <- readRDS(here::here("output", "postBurnIn_IITA_GS_2Yrs.rds"))
IITA3Yr <- readRDS(here::here("output", "postBurnIn_IITA_GS_3Yrs.rds"))

forSimPlotIITA_1_3_F1 <- IITAPS %>%
  mutate(YearAsCand = "PS") %>%
  bind_rows(IITAPSPlus %>%
              mutate(YearAsCand = "PS+")) %>% 
  bind_rows(IITA1Yr %>%
              mutate(YearAsCand = "1")) %>%
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "2")) %>%
  bind_rows(IITA3Yr %>% 
              mutate(YearAsCand = "3")) %>%
  unnest_longer(SimOutput) %>%
  filter(SimOutput_id == "records") %>%
  mutate(records = SimOutput) %>%
  select(SimRep, YearAsCand, records) %>% 
  unnest_longer(records) %>%
  filter(records_id == "stageOutputs") %>%
  mutate(stageOutputs = records) %>%
  select(SimRep, YearAsCand, stageOutputs) %>%
  unnest(cols = stageOutputs) %>%
  mutate(YearPostBurnIn = year - 40) %>% 
  filter(stage == "F1", YearPostBurnIn >= -5) %>%
  select(SimRep, YearAsCand, year, cycle, stage, genValMean, genValSD, YearPostBurnIn)

forSimPlotIITA_1_3_UYT <- IITAPS %>%
  mutate(YearAsCand = "PS") %>%
  bind_rows(IITAPSPlus %>%
              mutate(YearAsCand = "PS+")) %>% 
  bind_rows(IITA1Yr %>%
              mutate(YearAsCand = "1")) %>%
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "2")) %>%
  bind_rows(IITA3Yr %>% 
              mutate(YearAsCand = "3")) %>%
  unnest_longer(SimOutput) %>%
  filter(SimOutput_id == "records") %>%
  mutate(records = SimOutput) %>%
  select(SimRep, YearAsCand, records) %>% 
  unnest_longer(records) %>%
  filter(records_id == "stageOutputs") %>%
  mutate(stageOutputs = records) %>%
  select(SimRep, YearAsCand, stageOutputs) %>%
  unnest(cols = stageOutputs) %>%
  mutate(YearPostBurnIn = year - 40) %>% 
  filter(stage == "UYT2", YearPostBurnIn >= -5) %>%
  select(SimRep, YearAsCand, year, cycle, stage, genValMean, genValSD, YearPostBurnIn)

forSimPlotIITA_Acc <- IITAPS %>%
  mutate(YearAsCand = "PS") %>%
  bind_rows(IITAPSPlus %>%
              mutate(YearAsCand = "PS+")) %>% 
  bind_rows(IITA1Yr %>% 
              mutate(YearAsCand = "1")) %>% 
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "2")) %>% 
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "3")) %>% 
  unnest_wider(SimOutput)  %>%
  select(SimRep, YearAsCand, records) %>% 
  unnest_wider(records) %>%
  select(SimRep, YearAsCand, CrossingBlock) %>%
  unnest(col = CrossingBlock) %>% 
  select(SimRep, YearAsCand, Year, cycle, grmSize, accPgSel, accClSel) %>%
  mutate(YearPostBurnIn = Year - 40, year = Year, .keep = "unused") %>% 
  filter(YearPostBurnIn >= -5)

forSimPlotIITA_1_3_CET <- IITAPS %>%
  mutate(YearAsCand = "PS") %>%
  bind_rows(IITAPSPlus %>%
              mutate(YearAsCand = "PS+")) %>% 
  bind_rows(IITA1Yr %>%
              mutate(YearAsCand = "1")) %>%
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "2")) %>%
  bind_rows(IITA3Yr %>% 
              mutate(YearAsCand = "3")) %>%
  unnest_longer(SimOutput) %>%
  filter(SimOutput_id == "records") %>%
  mutate(records = SimOutput) %>%
  select(SimRep, YearAsCand, records) %>% 
  unnest_longer(records) %>%
  filter(records_id == "stageOutputs") %>%
  mutate(stageOutputs = records) %>%
  select(SimRep, YearAsCand, stageOutputs) %>%
  unnest(cols = stageOutputs) %>%
  mutate(YearPostBurnIn = year - 40) %>% 
  filter(stage == "CET", YearPostBurnIn >= -5) %>%
  select(SimRep, YearAsCand, year, cycle, stage, accAtSel, YearPostBurnIn)

forSimPlotIITA_Acc2 <- forSimPlotIITA_Acc %>%
  left_join(forSimPlotIITA_1_3_CET,
            by = c("SimRep", "YearAsCand", "year", "YearPostBurnIn"))

forSimPlotIITA_Par <- IITAPS %>%
  mutate(YearAsCand = "PS") %>%
  bind_rows(IITAPSPlus %>%
              mutate(YearAsCand = "PS+")) %>% 
  bind_rows(IITA1Yr %>% 
              mutate(YearAsCand = "1")) %>% 
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "2")) %>% 
  bind_rows(IITA2Yr %>% 
              mutate(YearAsCand = "3")) %>% 
  unnest_wider(SimOutput) %>%
  select(SimRep, YearAsCand, records) %>% 
  unnest_wider(records) %>%
  select(SimRep, YearAsCand, CrossingBlock) %>%
  unnest(cols = CrossingBlock) %>% 
  select(SimRep, YearAsCand, Year, cycle, grmData) %>%
  unnest(grmData) %>%
  mutate(YearPostBurnIn = Year - 40) %>%
  filter(pop == "c", YearPostBurnIn >=-5)

forSimPlotIITA_Par$stage <- schemeDF$stageNames[forSimPlotIITA_Par$stage]



saveRDS(forSimPlotIITA_Acc2, file = here::here("DataSimPlotIITA1_3_Acc.rds"))
saveRDS(forSimPlotIITA_Par, file = here::here("DataSimPlotIITA1_3_Par.rds"))
saveRDS(forSimPlotIITA_1_3_F1, file = here::here("DataSimPlotIITA1_3_F1.rds"))
saveRDS(forSimPlotIITA_1_3_UYT, file = here::here("DataSimPlotIITA1_3_UYT2.rds"))
```

[Home](VD_Optimization.html)
