---
title: "IITA Breeding Scheme"
author: "LucianoRogerio"
date: "2022-01-26"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


## Simulations with the IITA Breeding Scheme

<br />

| FunctionsArg  | FunctionName         |
| :-----------: | :------------------: |
| selCritPop    | parentSelCritBLUP    |
| selCritPipe   | productSelCritBLUP   |
| productFunc   | productPipeline      |
| popImprovFunc | popImprovByParentSel |
|               |                      |

<br />

#### Open R inside a singularity container

```{bash, eval = F}
screen -R LucianoSim;

# as I runned on Robbins Server I got to ask access to slurm

salloc -n 8 --mem 80G;

cd /workdir/lbraatz

singularity shell -B /programs rocker3.sif

R
```


#### Run R inside a singularity container

```{r, eval = F}

.libPaths(c(.libPaths(), "/programs/R-4.1.2/library/", "/home/lbraatz/R/x86_64-pc-linux-gnu-library/4.1/"))


library(devtools)
library(AlphaSimR)
library(AlphaSimHlpR)

suppressMessages(library(tidyverse))
suppressMessages(library(genomicMateSelectR))
library(dplyr); library(furrr); library(here)
library(RhpcBLASctl)

select <- dplyr::select
mutate <- dplyr::mutate

schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")

bsp1 <- specifyBSP(schemeDF = schemeDF,
                   nTrainPopCycles = 8, nYrsAsCandidates = 3, maxTrainingPopSize = 5120,
                   nChr = 18, effPopSize = 200, quickHaplo = F,
                   segSites = 1650, nQTL = 1000, nSNP = 500, genVar = 1500,
                   gxeVar = NULL, gxyVar = 1500, gxlVar = 750, gxyxlVar = 300,
                   meanDD = 0.23, varDD = 0.05, relAA = 0.5,
                   stageToGenotype = "AYT",  RmStagePhen = "SDN",
                   nParents = 100, nCrosses = 400, nProgeny = 30, nClonesToNCRP = 3,
                   parentsFlowering = 66,
                   phenoF1toStage1 = T, errVarPreStage1 = 17500,
                   useCurrentPhenoTrain = F,
                   nCyclesToKeepRecords = 4,
                   selCritPipeAdv = selCritIID,
                   selCritPopImprov =  selCritIID)

source(here::here("code","runSchemesPostBurnIn.R"))

nRepT <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% nrow()
NCT <- RhpcBLASctl::get_num_procs()
nRepMap <- 10
reps <- c(rep(1:ceiling(nRepT/nRepMap), each = nRepMap))[1:nRepT]


set.seed(501)

for(i in 1:max(reps)) {

burnIn_IITA_PS <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% .[reps==i,]
start <- proc.time()[3]
postBurnIn_IITA_PS <- runSchemesPostBurnIn(simulations = burnIn_IITA_PS,
                                           newBSP = bsp1,
                                           nPostBurnInCycles = 12,
                                           selCritPop = "parentSelCritBLUP",
                                           selCritPipe = "productSelCritBLUP",
                                           productFunc = "productPipelinePostBurnIn",
                                           popImprovFunc = "popImprovByParentSel",
                                           nSimCores = nRepMap,
                                           nBLASthreads = ifelse(test = ((NCT %% nrow(burnIn_IITA_PS)) == 0),
                                                            yes = floor((NCT - 1) / nrow(burnIn_IITA_PS)),
                                                            no = floor(NCT / nrow(burnIn_IITA_PS))))
end <- proc.time()[3]; print(paste0(floor((end - start)/60), "mins ", floor(((end - start)%%60)), "s elapsed - bspP"))

RdsName <- paste("postBurnIn_IITA_PS", i, ".rds", sep = "")
saveRDS(postBurnIn_IITA_PS,file = here::here("output", RdsName))
rm(postBurnIn_IITA_PS); rm(RdsName); rm(burnIn_IITA_PS)
}
```

```
 ****** 1 to 8
 [1] "25mins 45s elapsed - bspP"

 ****** 9 to 16
 [1] "25mins 52s elapsed - bspP"

 ****** 17 to 24


 ****** 25 to 32
 [1] "26mins 18s elapsed - bspP"

 ****** 33 to 40
 [1] "25mins 54s elapsed - bspP"
 
```


joint all the Results in a same rds File
```{r, eval = FALSE}
suppressMessages(library(tidyverse))
RhpcBLASctl::blas_set_num_threads(80)
files <- dir()[grep(pattern = "postBurnIn_IITA_PS*", dir())]
SimResults <- NULL
for(i in files){
  Results <- readRDS(i)
  SimResults <- rbind(SimResults, Results)  
  rm(Results)
}

saveRDS(SimResults, file = "postBurnIn_IITA_PS.rds")
rm(SimResults)
```
####  With Genomic Selection
<br />

| FunctionsArg  | FunctionName         |
| :-----------: | :------------------: |
| selCritPop    | parentSelCritGEBV    |
| selCritPipe   | productSelCritBLUP   |
| productFunc   | productPipeline      |
| popImprovFunc | popImprovByParentSel |
|               |                      |

###### Parameters Changuing in different scenarios

- nTrainPoCycles -> 8  - Server cbsulm14

<br />

```{r, eval = F}

schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")

bsp1 <- specifyBSP(schemeDF = schemeDF,
                   nTrainPopCycles = 8, nYrsAsCandidates = 3, maxTrainingPopSize = 5120,
                   nChr = 18, effPopSize = 200, quickHaplo = F,
                   segSites = 1650, nQTL = 1000, nSNP = 500, genVar = 1500,
                   gxeVar = NULL, gxyVar = 1500, gxlVar = 750, gxyxlVar = 300,
                   meanDD = 0.23, varDD = 0.05, relAA = 0.5,
                   stageToGenotype = "CET",
                   RmStagePhen = "SDN",
                   nParents = 100, nCrosses = 400, nProgeny = 30, nClonesToNCRP = 3,
                   parentsFlowering = 66,
                   phenoF1toStage1 = T, errVarPreStage1 = 17500,
                   useCurrentPhenoTrain = F,
                   nCyclesToKeepRecords = 12,
                   selCritPipeAdv = selCritIID,
                   selCritPopImprov =  selCritIID)

source(here::here("code","runSchemesPostBurnIn.R"))

nRepT <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% nrow()
NCT <- RhpcBLASctl::get_num_procs()
nRepMap <- 8
reps <- c(rep(1:ceiling(nRepT/nRepMap), each = nRepMap))[1:nRepT]

for(i in 1:ceiling(nRepT/nRepMap)) {

burnIn_IITA_PS <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% .[reps==i,]
start <- proc.time()[3]
postBurnIn_IITA_GS <- runSchemesPostBurnIn(simulations = burnIn_IITA_PS,
                                           newBSP = bsp1,
                                           nPostBurnInCycles = 12,
                                           selCritPop = "parentSelCritGEBV",
                                           selCritPipe = "productSelCritBLUP",
                                           productFunc = "productPipelinePostBurnIn",
                                           popImprovFunc = "popImprovByParentSel",
                                           nSimCores = nRepMap,
                                           nBLASthreads = ifelse(test = ((NCT %% nrow(burnIn_IITA_PS)) == 0),
                                                            yes = floor((NCT - 1) / nrow(burnIn_IITA_PS)),
                                                            no = floor(NCT / nrow(burnIn_IITA_PS))))
end <- proc.time()[3]; print(paste0(floor((end - start)/60), "mins ", floor(((end - start)%%60)), "s elapsed - bspP"))

RdsName <- paste("postBurnIn_IITA_GS", i, ".rds", sep = "")
saveRDS(postBurnIn_IITA_GS,file = here::here("output", RdsName))
rm(postBurnIn_IITA_GS); rm(RdsName); rm(burnIn_IITA_PS)
}
```

```
 ****** 1 to 7
 [1] "112mins 19s elapsed - bspP"

 ****** 8 to 14
 [1] "102mins 12s elapsed - bspP"

 ****** 15 to 21
 [1] "106mins 50s elapsed - bspP"

 ****** 22 to 28
 [1] "120mins 1s elapsed - bspP"

 ****** 29 to 35
 [1] "118mins 11s elapsed - bspP"

 ****** 36 to 40 
 [1] "91mins 51s elapsed - bspP"
```

joint all the Results in a same rds File
```{r, eval = FALSE}
suppressMessages(library(tidyverse))
RhpcBLASctl::blas_set_num_threads(80)
files <- dir()[grep(pattern = "postBurnIn_IITA_GS*", dir())]
SimResults <- NULL
for(i in files){
  Results <- readRDS(i)
  SimResults <- rbind(SimResults, Results)  
  rm(Results)
}

saveRDS(SimResults, file = "postBurnIn_IITA_GS.rds")
rm(SimResults)
```

### Obtain the ratio of Parent selected per stage

```{r Parent Selection origin, eval = FALSE}
library(tidyverse); library(AlphaSimR)
library(here)
schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")
simulations <- readRDS(here::here("output", "postBurnIn_IITA_GS.rds"))

RelPar <- tibble()
for(repl in 1:nrow(simulations)){
  
  F1s <- tibble(id = simulations$SimOutput[[repl]]$records$F1@id,
                mother = simulations$SimOutput[[repl]]$records$F1@mother,
                father = simulations$SimOutput[[repl]]$records$F1@father,
                Year = simulations$SimOutput[[repl]]$records$F1@fixEff,
                gv = simulations$SimOutput[[repl]]$records$F1@gv)
  
  
  for(year in 1:length(simulations$SimOutput[[repl]]$records$SDN)){
    
    progeny <- tibble(simulations$SimOutput[[repl]]$records$SDN[[year]],
                      Year = year) %>% filter(isChk != "check")
    parents <- tibble(id = unique(union(progeny$father,progeny$mother)) %>% .[order(as.numeric(.))])
    
    ProgenyInfo <- progeny %>% select(id) %>% left_join(F1s, by = "id") %>% select(c(id,Year))
    ParentsInfo <- parents %>% left_join(F1s, by = "id") %>% select(c(id, Year, gv))
    
    RelParent <- tibble(Replicate = repl, 
                        YearProgeny = unique(ProgenyInfo$Year),
                        StageParents = schemeDF$stageNames[unique(ProgenyInfo$Year) - as.numeric(names(table(ParentsInfo$Year)))],
                        NumberParents = table(ParentsInfo$Year),
                        ParentsDt = list(ParentsInfo))
    RelPar <- bind_rows(RelPar, RelParent)
    rm(RelParent)
  }
}

write.table(x = RelPar, file = here::here("output", "ParentOriginGS.csv"),
            sep = ",", quote = FALSE,
            row.names = FALSE, col.names = TRUE)
```


```{r}
IITAF1 <- postBurnInIITAGS %>% 
              mutate(PostBurnIn = "GS") %>% 
              bind_rows(postBurnInIITAPS %>% 
              mutate(PostBurnIn = "PS")) %>% 
              unnest_longer(SimOutput) %>%
              filter(SimOutput_id == "records") %>%
              mutate(records = SimOutput) %>%
              select(SimRep, PostBurnIn, records) %>% 
              unnest_longer(records) %>%
              filter(records_id == "F1") %>%
              mutate(F1Pop = records) %>%
  dplyr::select(SimRep, PostBurnIn, F1Pop) %>%
  unnest(F1Pop)

saveRDS(IITAF1, here::here("output", "IITA_F1.rds"))
rm(IITAF1)

IITAF1Data <- tibble()
for(i in 1:nrow(IITAF1)){
Data <- tibble(SimRep = IITAF1$SimRep[i],
               PostBurnIn = IITAF1$PostBurnIn[i],
               id = IITAF1$F1Pop[[i]]@id,
               gv = IITAF1$F1Pop[[i]]@gv)
IITAF1Data <- bind_rows(IITAF1Data, Data)
rm(Data)
}
saveRDS(IITAF1Data, here::here("output", "IITA_F1.rds"))
rm(IITAF1)
```
- Optimal Contribution - Server cbsulm34

<br />

```{r, eval = F}

schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")

bsp1 <- specifyBSP(schemeDF = schemeDF,
                   nTrainPopCycles = 8, nYrsAsCandidates = 3, maxTrainingPopSize = 5120,
                   nChr = 18, effPopSize = 200, quickHaplo = F,
                   segSites = 1650, nQTL = 1000, nSNP = 500, genVar = 1500,
                   gxeVar = NULL, gxyVar = 1500, gxlVar = 750, gxyxlVar = 300,
                   meanDD = 0.23, varDD = 0.05, relAA = 0.5,
                   stageToGenotype = "CET",
                   RmStagePhen = "SDN",
                   useOptContrib = TRUE, targetEffPopSize = 80, nCandOptCont = 500,
                   nParents = 100, nCrosses = 400, nProgeny = 30, nClonesToNCRP = 3,
                   parentsFlowering = 66,
                   phenoF1toStage1 = T, errVarPreStage1 = 17500,
                   useCurrentPhenoTrain = F,
                   nCyclesToKeepRecords = 12,
                   selCritPipeAdv = selCritIID,
                   selCritPopImprov =  selCritIID)

source(here::here("code","runSchemesPostBurnIn.R"))

nRepT <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% nrow()
NCT <- RhpcBLASctl::get_num_procs()
nRepMap <- 8
reps <- c(rep(1:ceiling(nRepT/nRepMap), each = nRepMap))[1:nRepT]

for(i in 1:ceiling(nRepT/nRepMap)) {

burnIn_IITA_PS <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% .[reps==i,]
start <- proc.time()[3]
postBurnIn_IITA_GS <- runSchemesPostBurnIn(simulations = burnIn_IITA_PS,
                                           newBSP = bsp1,
                                           nPostBurnInCycles = 12,
                                           selCritPop = "parentSelCritGEBV",
                                           selCritPipe = "productSelCritBLUP",
                                           productFunc = "productPipelinePostBurnIn",
                                           popImprovFunc = "popImprovByParentSel",
                                           nSimCores = nRepMap,
                                           nBLASthreads = ifelse(test = ((NCT %% nrow(burnIn_IITA_PS)) == 0),
                                                            yes = floor((NCT - 1) / nrow(burnIn_IITA_PS)),
                                                            no = floor(NCT / nrow(burnIn_IITA_PS))))
end <- proc.time()[3]; print(paste0(floor((end - start)/60), "mins ", floor(((end - start)%%60)), "s elapsed - bspP"))

RdsName <- paste("postBurnIn_IITA_GS", i, ".rds", sep = "")
saveRDS(postBurnIn_IITA_GS,file = here::here("output", RdsName))
rm(postBurnIn_IITA_GS); rm(RdsName); rm(burnIn_IITA_PS)
}
```

```
 ****** 1 to 7
 [1] "112mins 19s elapsed - bspP"

 ****** 8 to 14
 [1] "102mins 12s elapsed - bspP"

 ****** 15 to 21
 [1] "106mins 50s elapsed - bspP"

 ****** 22 to 28
 [1] "120mins 1s elapsed - bspP"

 ****** 29 to 35
 [1] "118mins 11s elapsed - bspP"

 ****** 36 to 40 
 [1] "91mins 51s elapsed - bspP"
```

joint all the Results in a same rds File
```{r, eval = FALSE}
suppressMessages(library(tidyverse))
RhpcBLASctl::blas_set_num_threads(80)
files <- dir()[grep(pattern = "postBurnIn_IITA_GS*", dir())]
SimResults <- NULL
for(i in files){
  Results <- readRDS(i)
  SimResults <- rbind(SimResults, Results)  
  rm(Results)
}

saveRDS(SimResults, file = "postBurnIn_IITA_GS.rds")
rm(SimResults)
```

### Obtain the ratio of Parent selected per stage

```{r Parent Selection origin, eval = FALSE}
library(tidyverse); library(AlphaSimR)
library(here)
schemeDF <- read.csv(here::here("data","baselineScheme - IITA.csv"), 
                     header = T, stringsAsFactors = F, sep = ";")
simulations <- readRDS(here::here("output", "postBurnIn_IITA_GS.rds"))

RelPar <- tibble()
for(repl in 1:nrow(simulations)){
  
  F1s <- tibble(id = simulations$SimOutput[[repl]]$records$F1@id,
                mother = simulations$SimOutput[[repl]]$records$F1@mother,
                father = simulations$SimOutput[[repl]]$records$F1@father,
                Year = simulations$SimOutput[[repl]]$records$F1@fixEff)
  
  
  for(year in 1:length(simulations$SimOutput[[repl]]$records$SDN)){
    
    progeny <- tibble(simulations$SimOutput[[repl]]$records$SDN[[year]],
                      Year = year) %>% filter(isChk != "check")
    parents <- tibble(id = unique(c(progeny$father,progeny$mother)) %>% .[order(as.numeric(.))])
    
    ProgenyInfo <- progeny %>% select(id) %>% left_join(F1s, by = "id") %>% select(c(id,Year))
    ParentsInfo <- parents %>% left_join(F1s, by = "id") %>% select(c(id, Year))
    
    RelParent <- tibble(Replicate = repl, 
                        YearProgeny = unique(ProgenyInfo$Year),
                        StageParents = schemeDF$stageNames[unique(ProgenyInfo$Year) - as.numeric(names(table(ParentsInfo$Year)))],
                        NumberParents = table(ParentsInfo$Year))
    RelPar <- bind_rows(RelPar, RelParent)
  }
}

write.table(x = RelPar, file = here::here("output", "ParentOriginGS.csv"),
            sep = ",", quote = FALSE,
            row.names = FALSE, col.names = TRUE)
```

[back](VD_Optimization.html)
