---
title: "New Variety Development Product 2"
author: "LucianoRogerio"
date: "2022-01-26"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


## Simulations with the IITA 2ยบ alternative breeding Scheme (Four years VDP)


###  Without Genomic Selection
<br />

| FunctionsArg  | FunctionName         |
| :-----------: | :------------------: |
| selCritPop    | parentSelCritBLUP    |
| selCritPipe   | productSelCritBLUP   |
| productFunc   | productPipeline      |
| popImprovFunc | popImprovByParentSel |
|               |                      |

<br />

```{r, eval = FALSE}

.libPaths(.libPaths(), "/programs/R-4.0.5/library/", "/home/lbraatz/R/x86_64-pc-linux-gnu-library/4.0/")


library(devtools)
library(progress); library(AlphaSimHlpR)
suppressMessages(library(tidyverse))
suppressMessages(library(genomicMateSelectR))
library(dplyr); library(furrr); library(here)

select <- dplyr::select
mutate <- dplyr::mutate

source(here::here("code","runSchemesPostBurnIn.R"))

NschemeDF2 <- read.csv(here::here("data","baselineScheme - IITA - NVDP2.csv"),
                     header = T, stringsAsFactors = F, sep = ";")

bsp2 <- specifyBSP(schemeDF = NschemeDF2,
                   nTrainPopCycles = 10, nYrsAsCandidates = 2, maxTrainingPopSize = 1000,
                   nChr = 18, effPopSize = 200, quickHaplo = F,
                   segSites = 1650, nQTL = 1000, nSNP = 500, genVar = 1500,
                   gxeVar = NULL, gxyVar = 1500, gxlVar = 750, gxyxlVar = 300,
                   meanDD = 0.23, varDD = 0.06, relAA = 0.5,
                   stageToGenotype = "CET",
                   nParents = 100, nCrosses = 400, nProgeny = 30, nClonesToNCRP = 3,
                   phenoF1toStage1 = T, errVarPreStage1 = 17500,
                   useCurrentPhenoTrain = F,
                   nCyclesToKeepRecords = 4,
                   selCritPipeAdv = selCritIID,
                   selCritPopImprov =  selCritIID)

nRepMap <- 5
nRepT <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% nrow()
reps <- c(rep(1:ceiling(nRepT/nRepMap), each = nRepMap))[1:nRepT]
NCT <- RhpcBLASctl::get_num_procs()  ## 40 cores



for(i in 1:ceiling(nRepT/nRepMap)) {

burnIn_IITA_PS <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% .[reps==i,]
start <- proc.time()[3]
postBurnIn_NVDP2_IITA_PS <- runSchemesPostBurnIn(simulations = burnIn_IITA_PS,
                                           newBSP = bsp2,
                                           nPostBurnInCycles = 12,
                                           selCritPop = "parentSelCritBLUP",
                                           selCritPipe = "productSelCritBLUP",
                                           productFunc = "productPipelinePostBurnIn",
                                           popImprovFunc = "popImprovByParentSel",
                                           nSimCores = nRepMap,
                                           nBLASthreads = ifelse(test = ((NCT %% nrow(burnIn_IITA_PS)) == 0),
                                                            yes = floor((NCT - 1) / nrow(burnIn_IITA_PS)),
                                                            no = floor(NCT / nrow(burnIn_IITA_PS))))
end <- proc.time()[3]; print(paste0(floor((end - start)/60), "mins ", floor(((end - start)%%60)), "s elapsed - bspP"))

RdsName <- paste("postBurnIn_NVDP2_IITA_PS", i, ".rds", sep = "")
saveRDS(postBurnIn_NVDP2_IITA_PS,file = here::here("output", RdsName))
rm(postBurnIn_NVDP2_IITA_PS); rm(RdsName); rm(burnIn_IITA_PS)
}
```

```
 ****** 6 to 10
[1] "14mins 7s elapsed - bspP"

 ****** 11 to 15
[1] "14mins 23s elapsed - bspP"

 ****** 16 to 20
[1] "14mins 12s elapsed - bspP"

 ****** 36 to 40
[1] "14mins 20s elapsed - bspP"
```



###  With Genomic Selection
<br />

| FunctionsArg  | FunctionName         |
| :-----------: | :------------------: |
| selCritPop    | parentSelCritGEBV    |
| selCritPipe   | productSelCritBLUP   |
| productFunc   | productPipeline      |
| popImprovFunc | popImprovByParentSel |
|               |                      |

<br />

```{r, eval = FALSE}

library(progress); library(AlphaSimHlpR)
suppressMessages(library(tidyverse))
suppressMessages(library(genomicMateSelectR))
library(dplyr); library(furrr); library(here)

select <- dplyr::select
mutate <- dplyr::mutate

source(here::here("code","runSchemesPostBurnIn.R"))

NschemeDF2 <- read.csv(here::here("data","baselineScheme - IITA - NVDP2.csv"),
                     header = T, stringsAsFactors = F, sep = ";")

bsp2 <- specifyBSP(schemeDF = NschemeDF2,
                   nTrainPopCycles = 10, nYrsAsCandidates = 2, maxTrainingPopSize = 1000,
                   nChr = 18, effPopSize = 200, quickHaplo = F,
                   segSites = 1650, nQTL = 1000, nSNP = 500, genVar = 1500,
                   gxeVar = NULL, gxyVar = 1500, gxlVar = 750, gxyxlVar = 300,
                   meanDD = 0.23, varDD = 0.06, relAA = 0.5,
                   stageToGenotype = "CET",
                   nParents = 100, nCrosses = 400, nProgeny = 30, nClonesToNCRP = 3,
                   phenoF1toStage1 = T, errVarPreStage1 = 17500,
                   useCurrentPhenoTrain = F,
                   nCyclesToKeepRecords = 4,
                   selCritPipeAdv = selCritIID,
                   selCritPopImprov =  selCritIID)

nRepMap <- 8
nRepT <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% nrow()
reps <- c(rep(1:ceiling(nRepT/nRepMap), each = nRepMap))[1:nRepT]
NCT <- RhpcBLASctl::get_num_procs()  ## 40 cores



for(i in 1:ceiling(nRepT/nRepMap)) {

burnIn_IITA_PS <- readRDS(here::here("output", "BurnIn_IITA.rds")) %>% .[reps==i,]
start <- proc.time()[3]
postBurnIn_NVDP2_IITA_GS <- runSchemesPostBurnIn(simulations = burnIn_IITA_PS,
                                           newBSP = bsp2,
                                           nPostBurnInCycles = 12,
                                           selCritPop = "parentSelCritGEBV",
                                           selCritPipe = "productSelCritBLUP",
                                           productFunc = "productPipelinePostBurnIn",
                                           popImprovFunc = "popImprovByParentSel",
                                           nSimCores = nRepMap,
                                           nBLASthreads = ifelse(test = ((NCT %% nrow(burnIn_IITA_PS)) == 0),
                                                            yes = floor((NCT - 1) / nrow(burnIn_IITA_PS)),
                                                            no = floor(NCT / nrow(burnIn_IITA_PS))))
end <- proc.time()[3]; print(paste0(floor((end - start)/60), "mins ", floor(((end - start)%%60)), "s elapsed - bspP"))

RdsName <- paste("postBurnIn_NVDP2_IITA_GS", i, ".rds", sep = "")
saveRDS(postBurnIn_NVDP2_IITA_GS,file = here::here("output", RdsName))
rm(postBurnIn_NVDP2_IITA_GS); rm(RdsName); rm(burnIn_IITA_PS)
}
```

```
 ****** 9 to 16
 [1] "148mins 3s elapsed - bspP"

 ****** 17 to 24
 [1] "163mins 15s elapsed - bspP"

 ****** 25 to 32
  [1] "162mins 39s elapsed - bspP"

 ****** 33 to 40
  [1] "168mins 57s elapsed - bspP"
```

[back](VD_Optimization.html)
