---
title: "Singularity Image"
author: "LucianoRogerio"
date: "2022-01-19"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---



## Install all the packages in our home library in BIOHPC home directory.

```{bash, eval = FALSE}
R
```

```{r, eval = FALSE}
library(devtools)

install_github(repo = "LucianoRogerio/AlphaSimHlpR", ref = "MarninPkg", force = TRUE)
path.package("AlphaSimHlpR")
# "/home/lbraatz/R/x86_64-pc-linux-gnu-library/4.0/AlphaSimHlpR"

# If you are going to use the asreml package for the genomic selection follow the following steps

library("asreml")
path.package("asreml")
# "/programs/R-4.0.5/library/asreml"

library(ASRgenomics)
path.package("ASRgenomics")
# "/home/lbraatz/R/x86_64-pc-linux-gnu-library/4.0/ASRgenomics"
```

## Create a Singularity Image from docker library of Images

```{bash, eval = FALSE}

screen -R LucianoSim;

# as I runned on Robbins Server I got to ask access to slurm

salloc -n 8 --mem 80G;

# Make a directory to save your Singularity image as backup
cd home/lbraatz/Desktop/;
mkdr Singularity;

singularity pull rocker2.sif docker://rocker/tidyverse:latest;

cp rocker2.sif /workdir/lbraatz/rocker2.sif

cd /workdir/lbraatz

singularity shell -B /programs rocker2.sif

R

```

## Add new R packages library to the R on the Singularity container

We are going to open R and add the your personal R packages libraries and the library of the High

```{r, eval = FALSE}

.libPaths(.libPaths(), "/programs/R-4.0.5/library/", "/home/lbraatz/R/x86_64-pc-linux-gnu-library/4.0/")

# Then try to call the asreml package from the Robbin's Server
library(asreml); library(ASRgenomics)

```
With all this codes we will be able to have access to the programs directory in Robbins Server, this will allows us to use asreml R package in our Simulations.

[Home](VD_Optimization.html)
