---
title: "Variety Development Product Optimization"
author: "Wolfemd, LucianoRogerio"
date: "2021-09-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

  We are simulating the expected genetic gains of IITA Breeding Scheme for their selection index to use as burn-in sim:
  
<br />

| logFYLD | HI  | DM  | MCMDS | logRTNO | logDYLD | logTOPYLD | PLTHT |
| :-----: | :-: | :-: | :---: | :-----: | :-----: | :-------: | :---: |
| 20x     | 10x | 15x | -10x  | 12x     | 20x     | 15x       | 10x   |
|         |     |     |       |         |         |           |       |
  
<br />  
  
  Marnin estimated the [genetic and error variances](https://wolfemd.github.io/IITA_2021GS/inputsForSimulationV2.html#Conclusions) for each trial type (CET, PYT, AYT, and UYT)
  
## Prepare the Singularity Image to run the Simulations on BioHPC servers

The steps to create the singularity image with all the required packages are described at this [link](SingularityIm.html).
  

### Breeding Scheme Simulations parameters

  The burn-in simulation were replicated 20 times, simulating a 26 cycles of operations with the burn-in of the first 20 cycles.

<br />

| Sim Parameter      | Value  |     | Genetic Parameter | Value  |     | Variances Parameters | Value  |
| :----------------: | :----: | :-: | :---------------: | :----: | :-: | :------------------: | :----: |
| nTrainPopCycles    | 3      |     | NChr              | 18     |     | genVar               | 1,500  |
| NYrsAsCandidates   | 3      |     | effPopsize        | 200    |     | gxeVar               | NULL   |
| maxTrainingPopSize | 1000   |     | segSites          | 1,650  |     | gxyVar               | 1,500  |
| stageToGenotype    | CET    |     | nQTL              | 1,000  |     | gxlVar               | 750    |
| nParents           | 100    |     | nSNP              | 500    |     | gxyxlVar             | 300    |
| nCrosses           | 400    |     |                   |        |     | meanDD               | 0.25   |
| nProgeny           | 25     |     |                   |        |     | varDD                | 0.05   |
| nClonesToNCRP      | 3      |     |                   |        |     | relAA                | 0.5    |
| phenoF1toStage1    | FALSE  |     |                   |        |     | errVarPreStage1      | 17,500 |
|                    |        |     |                   |        |     |                      |        |
  
<br />  

## Breeding Schemes scenarios

### IITA breeding Scheme
```{r IITA Breeding Scheme, message=FALSE, warning=FALSE}
library(tidyverse); library(reactable)
IITAScheme <- read.table(here::here("data", "baselineScheme - IITA.csv"),
                         sep = ";", dec = ".", header = T)
IITAScheme %>% reactable()
```

Simulations for IITA [breeding Scheme](IITABS.html)

### IITA 1ยบ alternative breeding Scheme (Five years VDP)
```{r IITA first alternative breeding scheme, message=FALSE, warning=FALSE}
library(tidyverse); library(reactable)
IITAScheme <- read.table(here::here("data", "baselineScheme - IITA - NVDP1.csv"),
                         sep = ";", dec = ".", header = T)
IITAScheme %>% reactable()
```

Simulations for IITA [1ยบ alternative breeding Scheme](NVDP1.html) (Five years VDP)

### IITA breeding Scheme 2ยบ alternative (Four years VDP)
```{r message=FALSE, warning=FALSE}
library(tidyverse); library(reactable)
IITAScheme <- read.table(here::here("data", "baselineScheme - IITA - NVDP2.csv"),
                         sep = ";", dec = ".", header = T)
IITAScheme %>% reactable()
```

Simulations for IITA [2ยบ alternative breeding Scheme](NVDP2.html) (Four years VDP)




### Simulations of IITA Breeding Scheme with clones selected as parent from different years as candidate

Scripts at this [link](1-3YrsIITABS.html)




## Simulation Results

The next simulation results were obtained with a G matrix of 10,000 clones.
While the Results of the simulations increasing the number of years [as candidate](#BreedingScheme1-3) have:

| YrsAsCand | G exp size |
| :-------: | :--------: |
| 1         | 3,502      |
| 2         | 6,002      |
| 3         | 8,502      |
|           |            |

#### Candidates Figure

```{r Figure 1 Candidates IITA Breeding Scheme 1 to 3 Yrs, fig.width=10, eval = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
library(here); suppressMessages(library(tidyverse)); library(ggpubr)

forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_Par.rds")) %>%
  filter(YearPostBurnIn >= -3) %>%
  mutate(CandPop = factor(ifelse(YearAsCand == 1, "CET",
                             ifelse(YearAsCand == 2, "CET-PYT",
                                    ifelse(YearAsCand == 3, "CET-AYT",
                                           ifelse(YearAsCand == "PS", "AYT-UYT2", "AYT-UYT2B")))),
                             levels = c("CET", "CET-PYT",
                                        "CET-AYT", "AYT-UYT2",
                                        "AYT-UYT2B")),
         SelMethod = factor(ifelse(CandPop %in% c("AYT-UYT2", "AYT-UYT2B"), "indBLUP", "GBLUP"))) %>%
  group_by(SimRep, CandPop, SelMethod, YearPostBurnIn) %>%
  summarise(bvMean = mean(bv),
            bvsd = sd(bv))

meanBVplot1 <- forSimPlot %>% 
              group_by(CandPop, SelMethod, YearPostBurnIn) %>%
              summarize(meanBVMean = mean(bvMean),
                        seBVMean = sd(bvMean) / sqrt(n())) %>% 
              ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) + 
              geom_ribbon(aes(ymin = meanBVMean - seBVMean, 
                              ymax = meanBVMean + seBVMean,
                              fill = CandPop), alpha = 0.25,) + 
              geom_line(aes(y = meanBVMean, color = CandPop)) + 
              theme_minimal() + ylab("Year") + theme(legend.position = "bottom") +
              labs(x = "Year",
                   y = expression(italic(mu[TBV] - "Pop")))

meanBVplot1
#sdBVplot1 <- forSimPlot %>% 
#              group_by(YearAsCand, YearPostBurnIn) %>%
#              summarize(meanBVsd = mean(bvsd),
#                        seBVsd = sd(bvsd) / sqrt(n())) %>% 
#              ggplot(., aes(x = YearPostBurnIn)) + 
#              geom_ribbon(aes(ymin = meanBVsd - seBVsd, 
#                              ymax = meanBVsd + seBVsd,
#                              fill = YearAsCand), alpha = 0.25) + 
#              geom_line(aes(y = meanBVsd, color = YearAsCand)) + 
#              theme_minimal() + ylab("Year")
#tiff(filename = here::here("output", "Figures", "Candidates graph 1 to 3.tiff"),
#units = "cm", compression = "lzw", width = 25, height = 15, res = 250)
#ggarrange(meanBVplot1, common.legend = TRUE, legend = "bottom") %>%
#  annotate_figure(., top = "Candidates Breeding Values")
#dev.off()
```

#### Parents Figure

```{r Figure 1 Parents IITA Breeding Scheme 1 to 3 Yrs, fig.width=10, echo = FALSE, message = FALSE, warning = FALSE}
library(here); suppressMessages(library(tidyverse)); library(ggpubr)

forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_Par.rds")) %>%
  filter(YearPostBurnIn >= -3) %>%
  mutate(CandPop = factor(ifelse(YearAsCand == 1, "CET",
                             ifelse(YearAsCand == 2, "CET-PYT",
                                    ifelse(YearAsCand == 3, "CET-AYT",
                                           ifelse(YearAsCand == "PS", "AYT-UYT2", "AYT-UYT2B")))),
                             levels = c("CET", "CET-PYT",
                                        "CET-AYT", "AYT-UYT2",
                                        "AYT-UYT2B")),
         SelMethod = factor(ifelse(CandPop %in% c("AYT-UYT2", "AYT-UYT2B"), "indBLUP", "GBLUP"))) %>%
  group_by(SimRep, CandPop, SelMethod, YearPostBurnIn) %>%
  slice_max(gebv, n = 30) %>%
  summarise(bvMean = mean(bv),
            bvsd = sd(bv))

meanBVplot1 <- forSimPlot %>% 
              group_by(CandPop, SelMethod, YearPostBurnIn) %>%
              summarize(meanBVMean = mean(bvMean),
                        seBVMean = sd(bvMean) / sqrt(n())) %>% 
              ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) +
              geom_ribbon(aes(ymin = meanBVMean - seBVMean, 
                              ymax = meanBVMean + seBVMean,
                              fill = CandPop), alpha = 0.25) + 
              geom_line(aes(y = meanBVMean, color = CandPop)) + 
              theme_minimal() + ylab("Year") + theme(legend.position = "bottom") +
              labs(x = "Year",
                   y = expression(italic(mu[TBV]) - "Top 30"))
meanBVplot1
#sdBVplot1 <- forSimPlot %>% 
#            group_by(CandPop, YearPostBurnIn) %>% 
#            summarize(meanBVSD = mean(bvsd),
#                      seBVSD = sd(bvsd) / sqrt(n())) %>% 
#            ggplot(., aes(x = YearPostBurnIn)) +
#            geom_ribbon(aes(ymin = meanBVSD - seBVSD, 
#                            ymax = meanBVSD + seBVSD,
#                            fill = CandPop), alpha = 0.25) + 
#            geom_line(aes(y = meanBVSD, color = CandPop)) + 
#            theme_minimal()
#
#tiff(filename = here::here("output", "Figures", "Parents graph 1 to 3.tiff"),
#units = "cm", compression = "lzw", width = 25, height = 15, res = 250)
#ggarrange(meanBVplot1, sdBVplot1, common.legend = TRUE, legend = "bottom") %>%
#  annotate_figure(., top = "Parents Breeding Values")
#dev.off()
```


#### Origin of the parents in each year

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(viridis)
forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_Par.rds")) %>%
  mutate(stage = factor(stage, levels = c("CET", "PYT", "AYT", "UYT1","UYT2")))

BoxPlotPar <- forSimPlot %>% 
  filter(YearPostBurnIn >= -3, !YearAsCand %in% c("PS", "PS+")) %>%
  mutate(CandPop = as.character(YearAsCand)) %>%
  group_by(SimRep, CandPop,YearPostBurnIn) %>%
  slice_max(gebv, n = 30) %>%
  mutate(YearPostBurnIn = factor(YearPostBurnIn, levels = c(-3:24)),
         CandPop = ifelse(CandPop == "1", "CET",
                             ifelse(CandPop == "2", "CET+PYT", "CET+PYT+AYT"))) %>%
  ggplot(aes(y = bv, x = YearPostBurnIn, fill = stage)) +
  geom_boxplot() + facet_wrap(~CandPop, scales = "free_x") +
  scale_fill_viridis(discrete = TRUE, option = "viridis") +
  theme_bw() + labs(y = expression(italic(TGV)) , x = "Year")

```


```{r Origin Parents, echo = FALSE, warning = FALSE, message = FALSE}
PO <- forSimPlot%>% 
  filter(YearPostBurnIn >= -3, !YearAsCand %in% c("PS", "PS+")) %>%
  mutate(CandPop = as.character(YearAsCand)) %>%
  group_by(SimRep, CandPop,YearPostBurnIn) %>%
  slice_max(gebv, n = 30) %>%
  mutate(YearPostBurnIn = factor(YearPostBurnIn, levels = c(-3:23)),
         CandPop = ifelse(CandPop == "1", "CET",
                             ifelse(CandPop == "2", "CET+PYT", "CET+PYT+AYT"))) %>%
  group_by(CandPop, YearPostBurnIn, stage, SimRep) %>%
  summarise(NParSel = n()) %>% group_by(CandPop, YearPostBurnIn, stage) %>%
  summarise(NParSelM = median(NParSel),
            NParSelMin = min(NParSel, na.rm = TRUE),
            NParSelMax = max(NParSel, na.rm = TRUE),
            NParSelsd = sd(NParSel, na.rm = TRUE))


BarPlotPO <- PO %>%
  ggplot(aes(x = YearPostBurnIn, fill = stage, y = NParSelM)) +
  geom_bar(position = "fill", stat = "identity", width = 0.7) + xlab("Year Post Burn in") +
  facet_wrap(~CandPop, scales = "free_x") +
  scale_fill_viridis(discrete = TRUE, option = "viridis") + theme_bw() +
  labs(y = expression(italic("Parent stage origin")),
       x = "Year")

#tiff(filename = here::here("output", "Figures", "ParentInfo.tiff"),
#units = "cm", compression = "lzw", width = 25, height = 15, res = 250)
ggarrange(BoxPlotPar, BarPlotPO, nrow = 2, ncol = 1, common.legend = TRUE, legend = "bottom") %>%
  annotate_figure(., top = "Parents Breeding Values Vs Origin")
#dev.off()
```



#### F1 Figure

```{r Figure 1 F1 IITA Breeding Scheme 1 to 3 Yrs, fig.width=10, echo = FALSE, message = FALSE, warning = FALSE}
library(here); suppressMessages(library(tidyverse)); library(ggpubr)

forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_F1.rds")) %>%
              filter(YearPostBurnIn >= -3) %>%
  mutate(CandPop = factor(ifelse(YearAsCand == 1, "CET",
                             ifelse(YearAsCand == 2, "CET-PYT",
                                    ifelse(YearAsCand == 3, "CET-AYT",
                                           ifelse(YearAsCand == "PS", "AYT-UYT2", "AYT-UYT2B")))),
                             levels = c("CET", "CET-PYT",
                                        "CET-AYT", "AYT-UYT2",
                                        "AYT-UYT2B")),
         SelMethod = factor(ifelse(CandPop %in% c("AYT-UYT2", "AYT-UYT2B"), "indBLUP", "GEBV")))

meanGplot1 <- forSimPlot %>% 
              group_by(CandPop, SelMethod, YearPostBurnIn, year) %>% 
              summarize(meanGenMean = mean(genValMean),
                        seGenMean = sd(genValMean) / sqrt(n())) %>% 
              ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) +
              geom_ribbon(aes(ymin = meanGenMean - seGenMean, 
                              ymax = meanGenMean + seGenMean,
                              fill = CandPop), alpha = 0.25) + 
              geom_line(aes(y = meanGenMean, color = CandPop)) + 
              theme_minimal() + labs(y = expression(italic("True GV")),
                                     x = "Year") + xlim(-3, 24) + ylim(400, 800)

sdGplot1 <- forSimPlot %>% 
            group_by(CandPop, SelMethod, YearPostBurnIn, year) %>% 
            summarize(meanGenSD = mean(genValSD),
                      seGenSD = sd(genValSD) / sqrt(n())) %>% 
            ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) +
            geom_ribbon(aes(ymin = meanGenSD - seGenSD, 
                            ymax = meanGenSD + seGenSD,
                            fill = CandPop), alpha = 0.25) + 
            geom_line(aes(y = meanGenSD, color = CandPop)) + 
            theme_minimal() + labs(y = expression(italic(sigma[TGV]^2)),
                                     x = "Year") + xlim(-3, 24)

#tiff(filename = here::here("output","Figures", "F1 graph 1 to 3.tiff"),
#units = "cm", compression = "lzw", width = 25, height = 15, res = 250)
ggarrange(meanGplot1, sdGplot1, common.legend = TRUE, legend = "bottom") %>% 
  annotate_figure(., top = "F1 Genotypic Values")
#dev.off()
```

#### UYT2 Figure

```{r Figure 1 UYT2 IITA Breeding Scheme 1 to 3 Yrs, fig.width=10, echo = FALSE, message = FALSE, warning = FALSE}
library(here); suppressMessages(library(tidyverse)); library(ggpubr)

forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_UYT2.rds")) %>%
  mutate(YearPostBurnIn = year - 20) %>%
              filter(YearPostBurnIn >= -3) %>%
  mutate(CandPop = factor(ifelse(YearAsCand == 1, "CET",
                             ifelse(YearAsCand == 2, "CET-PYT",
                                    ifelse(YearAsCand == 3, "CET-AYT",
                                           ifelse(YearAsCand == "PS", "AYT-UYT2", "AYT-UYT2B")))),
                             levels = c("CET", "CET-PYT",
                                        "CET-AYT", "AYT-UYT2",
                                        "AYT-UYT2B")),
         SelMethod = factor(ifelse(CandPop %in% c("AYT-UYT2", "AYT-UYT2B"), "indBLUP", "GEBV")))

meanGplot1 <- forSimPlot %>%
              group_by(CandPop, SelMethod, YearPostBurnIn, year) %>% 
              summarize(meanGenMean = mean(genValMean),
                        seGenMean = sd(genValMean) / sqrt(n())) %>% 
              ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) +
              geom_ribbon(aes(ymin = meanGenMean - seGenMean, 
                              ymax = meanGenMean + seGenMean,
                              fill = CandPop), alpha = 0.25) + 
              geom_line(aes(y = meanGenMean, color = CandPop)) + 
              theme_minimal() + labs(y = expression(italic("True GV")),
                                     x = "Year")

sdGplot1 <- forSimPlot %>%
            group_by(CandPop, SelMethod, YearPostBurnIn, year) %>% 
            summarize(meanGenSD = mean(genValSD),
                      seGenSD = sd(genValSD) / sqrt(n())) %>% 
            ggplot(., aes(x = YearPostBurnIn, linetype = SelMethod)) +
            geom_ribbon(aes(ymin = meanGenSD - seGenSD, 
                            ymax = meanGenSD + seGenSD,
                            fill = CandPop), alpha = 0.25) + 
            geom_line(aes(y = meanGenSD, color = CandPop)) + 
            theme_minimal() + labs(y = expression(italic(sigma[TGV]^2)),
                                   x = "Year")

#tiff(filename = here::here("output", "Figures", "UYT2 graph 1 to 3.tiff"),
#units = "cm", compression = "lzw", width = 25, height = 15, res = 250)
ggarrange(meanGplot1, sdGplot1, common.legend = TRUE, legend = "bottom") %>%
  annotate_figure(., top = "Last Trial Genotypic Values")
#dev.off()
```

##### Genomic Prediction Accuracy for the Candidates

```{r Accuracies for gebv, echo = FALSE, message = FALSE, warning = FALSE}

forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_AccPg.rds")) %>%
  filter(YearPostBurnIn >= -3) %>%
  mutate(CandPop = factor(ifelse(YearAsCand == 1, "CET",
                             ifelse(YearAsCand == 2, "CET-PYT",
                                    ifelse(YearAsCand == 3, "CET-AYT",
                                           ifelse(YearAsCand == "PS", "AYT-UYT2", "AYT-UYT2B")))),
                             levels = c("CET", "CET-PYT",
                                        "CET-AYT", "AYT-UYT2",
                                        "AYT-UYT2B")),
         SelMethod = factor(ifelse(CandPop %in% c("AYT-UYT2", "AYT-UYT2B"), "indBLUP", "GBLUP")))

Accuracyplot2 <- forSimPlot %>%
  group_by(CandPop, SelMethod, YearPostBurnIn, year) %>%
  summarise(meanAcc = mean(accPgSel, na.rm = T),
            sdAcc = sd(accPgSel, na.rm = T) / sqrt(n())) %>%
  ggplot(., aes(x = YearPostBurnIn, color = CandPop, linetype = SelMethod)) +
  geom_ribbon(aes(ymin = meanAcc - sdAcc, 
                  ymax = meanAcc + sdAcc,
                  fill = CandPop), alpha = 0.25) + 
  geom_line(aes(y = meanAcc)) + ggtitle("Parent Selection Accuracy") + 
  theme_minimal() + theme(legend.position="bottom") + ylim(0,0.75) +
  labs(y = expression(italic("Correlation - True BV")),
       x = "Year")

#tiff(filename = here::here("output", "Figures", "Accuracy.tiff"),
#units = "cm", compression = "lzw", width = 20, height = 10, res = 250)
Accuracyplot2
#dev.off()

```

##### Genomic Prediction Accuracy for clone selection at the CET

```{r Accuracies for gegv, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse); library(ggpubr)
forSimPlot <- readRDS(here::here("output", "DataSimPlotIITA1_3_AccCl.rds")) %>%
  filter(YearPostBurnIn >= -3, year != 64, stage != "UYT2") %>%
  mutate(Pred = ifelse(SimStage == "PopImprov", "GEBV", "indBLUP"),
         stage = factor(stage, levels = c("CET", "PYT", "AYT", "UYT1")), .keep = "unused") %>% 
  select(SimRep, YearPostBurnIn, year, cycle, Pred, stage, accAtSel) %>%
  filter(!is.na(accAtSel), !(Pred == "GEBV" & YearPostBurnIn < 0))



Accuracyplot2 <- forSimPlot %>%
  group_by(Pred, stage, YearPostBurnIn, year) %>%
  summarise(meanAcc = mean(accAtSel, na.rm = T),
            sdAcc = sd(accAtSel, na.rm = T) / sqrt(n())) %>%
  ggplot(., aes(x = YearPostBurnIn, color = Pred)) +
  geom_ribbon(aes(ymin = meanAcc - sdAcc, 
                  ymax = meanAcc + sdAcc,
                  fill = Pred), alpha = 0.25) + 
  geom_line(aes(y = meanAcc)) + facet_wrap(~stage, ncol = 2) + ggtitle("Clone Selection Accuracy") + 
  theme_minimal() + theme(legend.position="bottom") + ylim(0,0.75) + xlim(-3, 24) +
  labs(y = expression(italic("Correlation - True GV")),
       x = "Year")

#tiff(filename = here::here("output", "Figures", "AccuracyCl.tiff"),
#     units = "cm", compression = "lzw", width = 20, height = 10, res = 250)
Accuracyplot2
#dev.off()

```


